\documentclass[11pt]{article}

\usepackage{hyperref}
\usepackage[letterpaper, top=1in, bottom=1in, left=1.5in, right=1in]{geometry}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{epstopdf}
\usepackage{pdfpages}
\usepackage[titletoc,title]{appendix}
\usepackage[nottoc,notbib]{tocbibind}
\usepackage{lipsum}
\usepackage[toc]{glossaries}
\usepackage{verbatim}
\usepackage{subcaption}
\usepackage{bookmark}
\usepackage{setspace}
\usepackage{titlesec}
\usepackage{setspace}

% Font
% Title and Heading Styling
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\definecolor{heading-color}{HTML}{1A8EBD}
\definecolor{subheading-color}{HTML}{333333}
\definecolor{subsubheading-color}{HTML}{666666}

\titleformat{\section}
  {\normalfont\sffamily\fontsize{16pt}{16}\bfseries\color{heading-color}}
  {\thesection}{1em}{}

\titleformat{\subsection}
  {\normalfont\sffamily\fontsize{14pt}{14}\bfseries\color{subheading-color}}
  {\thesubsection}{1em}{}
\titleformat{\subsubsection}
  {\normalfont\sffamily\fontsize{14pt}{14}\bfseries\color{subsubheading-color}}
  {\thesubsubsection}{1em}{}

% Section Tweaks
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\renewcommand{\abstractname}{Executive Summary}

\usepackage{etoolbox}
\patchcmd{\thebibliography}{\section*{\refname}}{}{}{}

\bookmarksetup{open,numbered}


%   Glossary
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\newglossaryentry{philipsHue}
{
  name=Philips Hue Light Bulb,
  description={A ``smart'' light bulb that connects
  to home Wi-Fi networks, \url{http://meethue.com/}}
}

\newacronym{api}{API}{Application Programming Interface}

\makeglossaries


%   _____                _     __  __       _   _            
%  |  ___| __ ___  _ __ | |_  |  \/  | __ _| |_| |_ ___ _ __ 
%  | |_ | '__/ _ \| '_ \| __| | |\/| |/ _` | __| __/ _ \ '__|
%  |  _|| | | (_) | | | | |_  | |  | | (_| | |_| ||  __/ |   
%  |_|  |_|  \___/|_| |_|\__| |_|  |_|\__,_|\__|\__\___|_|   
%



\begin{document}

\raggedright
\doublespacing

\pagenumbering{gobble}

%   Letter of Transmittal
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    %\pdfbookmark[section]{Letter of Transmittal}{lot}
    %\includepdf{../"Letter of Transmittal"/"Letter of Transmittal".pdf}
   

%   Cover Page
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    
%    \pdfbookmark[section]{Cover Page}{cover}
%    \includepdf{Pages/CoverPage.pdf}


%   Table of Contents and Figures 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \setcounter{page}{1}
    \pagenumbering{roman}
    

\setlength{\parskip}{1mm}   
    
    \pdfbookmark[section]{\contentsname}{toc}
    \tableofcontents
    \newpage
    

\setlength{\parskip}{2mm}   
    
    
    \phantomsection
    \listoffigures
    \newpage
    
    \printglossaries
    \newpage
        
%   Summary 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    
\begin{abstract}
\phantomsection
\addcontentsline{toc}{section}{Executive Summary}
\noindent  

% TODO: BEN - Abstract

\end{abstract}
\newpage

%   ____            _       
%  | __ )  ___   __| |_   _ 
%  |  _ \ / _ \ / _` | | | |
%  | |_) | (_) | (_| | |_| |
%  |____/ \___/ \__,_|\__, |
%                     |___/ 
    
    
\setcounter{page}{1}
\pagenumbering{arabic}
\glsresetall
\renewcommand{\arraystretch}{1.5} % Fix the table sizes
    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    
%
% INTRODUCTION
% ---------------------------------------
\section{Introduction}\label{introduction}

% TODO: BEN - Introduction

%
% PROBLEM DEFINITION
% ---------------------------------------
\section{Problem Description}\label{problem-description}

Here at Softstart software incubator we make great ideas happen.
\textbf{Good Morning} is an app that will help users wake up in the
morning. It will also help them stay informed by informing them of
goings on when they wake up.

% TODO: ANDREI - Problem Definition

%
% PROJECT OBJECTIVES
% ---------------------------------------
\section{Project Objectives}\label{project-objectives}

There are several key objectives that make up \textbf{Good Morning},

\begin{itemize}
\item
  A core alarm application
\item
  A smart assistant to tell you Weather, Missed Messages etc.
\item
  Flexibility to learn/integrate your morning schedule
\item
  Smart integration, e.g. a \glslink{philipsHue}{Philips Hue wakeup light}
\end{itemize}

% TODO: JAKE - Project Objectives

%
% CURRENT SYSTEMS
% ---------------------------------------
\section{Current Systems}\label{current-systems}

Softstart believes that \textbf{Good Morning} has the potential to fill
a sizeable market niche that is currently vacant. There are currently no other all-in-one systems
for boosting morning productivity. There are however some other applications
on the market that provide similar tools and functions.

Wake Up Applications: There are many different wake up applications on the market, most
of which are simple alarm clocks, the following are a few of the more popular and unique ones in use.
\begin{itemize}
\item
    \textbf{Sleep Cycle}: Sleep cycle is a simple alarm clock that monitors your sleep
    cycle, and wakes you up during the lightest part of your sleep.
\item
    \textbf{iCuckoo}: This alarm application makes a donation to a charity of your choice every time you hit the
    the snooze button.
\item
    \textbf{Wakie}: Wakie is a different but unique approach to waking up. It
    involves two anonymous users. Users are either wakies or sleepyheads. 
    The sleepyheads determine what time they would like to wake up and how they would
    like to be woken up. Then the wakies will contact them at the specified time and 
    discuss whatever topic the sleepyhead specified. The wakies only have 1 minute to
\item
	\textbf{Google Now}: Google Now provides useful information based on your current location, frequently
	visited locations, and search history. It provides a lot of useful and relevant information to users 
	depending on the time of day.
\end{itemize}

\textbf{Good Morning} will provide users with many of the tools that the above applications
provide, but package them all together with an easy to use interface. On top of that, it will also
interact with other systems through the internet of things, allowing users to have even more flexibility 
and utility. No other applications have achieved this yet


% TODO: JONAH - Current Systems

%
% TARGET USERS
% ---------------------------------------
\section{Target Users}\label{target-users}

The target audience will be adults ages 18 -- 32. They will use it as a
personal organization tool.

% TODO: JAKE - Target Users

%
% KNOWN INTERACTIONS
% ---------------------------------------
\section{Known Interactions}\label{known-interactions}

\begin{itemize}
\item
  Smart devices, e.g. \gls{philipsHue}
\item
  Mobile Operating System and \glspl{api}, i.e., Android or iOS
\end{itemize}

% TODO: ANDREI - Known Interactions

%
% Known Contraints
% ---------------------------------------
\section{Known Constraints}\label{known-constraints}

\begin{itemize}
 \item Internationalization
 \item The app must be easy to use
\end{itemize}

% TODO: JONAH - Constaints

%
% Project Schedule
% ---------------------------------------
\section{Project Schedule}\label{project-schedule}

% TODO: BEN - Project Schedule

%\begin{longtable}[c]{@{}ll@{}}
%\toprule
%\textbf{Project Milestone} & \textbf{Date}\tabularnewline
%\midrule
%\endhead
%\textbf{Draft Requirements Definition } & 21 Jan\tabularnewline
%\textbf{Promotional Website Live } & 21 Jan\tabularnewline
%\textbf{Formal Requirements Definition (Revision) } & 16
%Feb\tabularnewline
%\textbf{Detailed Requirements Definition (Revision) } & 1
%Mar\tabularnewline
%\textbf{Preliminary Prototype Demo } & 3 Mar\tabularnewline
%\textbf{Final Requirements Definition (Revision) } & 15
%Mar\tabularnewline
%\textbf{User Manual } & 22 Mar\tabularnewline
%\textbf{Final Prototype Demo } & 31 Mar\tabularnewline
%\hrule
%\end{longtable}


%
% PROJECT TEAM
% ---------------------------------------
\section{Project team}\label{project-team}

% TODO: BEN - Project Team


    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
    \pagebreak
    \section{References} 
    
    \bibliographystyle{IEEEtran}

    \bibliography{references}
    
    \pagebreak
%   ____             _      __  __       _   _            
%  | __ )  __ _  ___| | __ |  \/  | __ _| |_| |_ ___ _ __ 
%  |  _ \ / _` |/ __| |/ / | |\/| |/ _` | __| __/ _ \ '__|
%  | |_) | (_| | (__|   <  | |  | | (_| | |_| ||  __/ |   
%  |____/ \__,_|\___|_|\_\ |_|  |_|\__,_|\__|\__\___|_|   
%  

% Appendices

%\pdfbookmark[part]{Appendices}{appx}
%\begin{appendices}
%
%\section{Tool Screen Captures}\label{appx:screens}
%
%
%\end{appendices}

\end{document}
